---
title: 'Title'
subtitle: "Subtitle"
author: "Your Name"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
    citation_package: natbib
bibliography: /Users/takaaki/Documents/GitHub/gis-data/RMarkdown/reference.bib
biblio-style: apa
link-citations: yes
fontsize: 11pt
classoption: a4paper
header-includes:
  \usepackage{url}
---

```{r setup, include=FALSE}
source('~/documents/GitHub/gis-data/R_Econometrics/.Rprofile')
```

# Section 1 (level 1)

In this section, we... 

## Subsection (level 2)

In this subsection, we...

### Sub-subsection (level 3)

In this sub-subsection, we...

The symbol \# makes the section title. Depending on the number of \#, you can create different levels of sections. 



# Background

## History of Japan

In this subsection, we...



# Citation

You can cite articles such as papers and reports using bibtex. If you save the reference called Greenstone2015, put this name after \@. For example, \@Greenstone2015 can produce the following: @Greenstone2015. If you use brackets [], it creates [@Donaldson2016]. Finally, when you want to cite multiple articles, sepalate the names using ;. It produces the following [@Greenstone2015; @Donaldson2016].


Note that you have to specify the citation style in the preamble of the Rmd. See this files preamble. 



# .Rprofile

.Rprofile can be executed by `source` with `include=FALSE` without showing the results in the output (like PDF). In this file I put the file path just after the preamble. It is very useful to run multiple `library` thet you often use. 



# Regression

We conduct regression without specifying the types of the standard error. 

## Set Up Data
```{r}
data(CASchools)   

# student teacher ratio
CASchools$STR <- CASchools$students / CASchools$teachers       

# average test score
CASchools$score <- (CASchools$read + CASchools$math)/2
```


This is same as: "reg score STR" in Stata. In R language we always need to specify which data will be used. 
```{r}
fit1 <- lm(score ~ STR, data = CASchools) 
summary(fit1) 
```


Present the equations. 
```{r, results='asis'}
equatiomatic::extract_eq(fit1)
equatiomatic::extract_eq(fit1, use_coefs = TRUE)
```

We can include further controls in the equation. 

```{r}
fit2 <- lm(score ~ STR + english + income, data = CASchools) 
summary(fit2) 
```


```{r, results='asis'}
equatiomatic::extract_eq(fit2)
equatiomatic::extract_eq(fit2, use_coefs = TRUE)
```



## Cluster Robust Standard Error

In empirical work we always deal with correlation within a group by clustering SE. Above lm code conduct regression under the assumption of homoskedasticity just like reg and without robust option in Stata. We now use the estimatr package. 


```{r}
fit3 <- estimatr::lm_robust(score ~ STR + english + income,
                            clusters = county, se_type = "stata",
                            data = CASchools) 
summary(fit3) 
```


We estimated the same model as fit2, but clustered SE at the county level (we do not know whether this is the best unit). Clustered SE for STR increased from 0.277 to 0.299. 


## (Automatically) Create Regression Tables

Like `outreg2` in Stata, there are several ways to create tables in R using latex. You can also make tables in the MS Word file if you speficy in the preamble. The most popular one is `stargazer`, but in some situations `texreg` and `Hmisc` are more convenient. 


## Produce the Regression Table (with `stargazer`)
```{r, results='asis', message=FALSE, warning=FALSE}
# Define removed unnecessary variables from the table

# Define the row names
label_regressors <- c("Student Teacher Ratio", "English Score", "Parents Income")

stargazer(fit1, fit2,
          se = starprep(fit1, fit2,
                        clusters = CASchools$county, 
                        se_type = "stata"),
          title = "OLS estimation", 
          dep.var.caption = "",
          dep.var.labels = "Dependent Variable Name Here",
          covariate.labels = label_regressors,
          omit.stat = c("adj.rsq", "f", "ser"),
          notes.append = FALSE, 
          # single.row = TRUE,
          digits = 4, 
          notes = "",
          notes.align = "c",
          # align = T,
          no.space = T,
          add.lines = list(
            c("Log of population", "", "Yes"),
            c("Temperature", "", "Yes"),
            c("Demographic characteristic", "Yes", "Yes"),
            c("Household wealth", "Yes", "Yes")),
          # table.layout ="-n",
          # font.size = "scriptsize"
          header = FALSE
          )
```
